Discrete Ordinates

### 2017-06-01 docprep/chapbib.tex
The table is now sideways
Added some MC notes

@@

\begin{table}[ht]
\caption{Water Regions}
\centering 
\begin{tabular}{l c r r r r r r r r r r r r}
\hline \hline   
Media       & CT Range      & H    & C    & N    & 0    & Na  & Mg  & P    & S   & Cl  & Ar  & K   & Ca \\ [0.5ex] 
\hline
Air         & -950 to -100  &      &      & 75.7 & 23.3 &     &     &      &     &     & 1.3 &     &      \\
Lung        & -1000 to -950 & 10.3 & 10.5 &  3.1 & 74.9 & 0.2 &     &  0.2 & 0.3 & 0.3 &     & 0.2 &      \\
Adipose     & -100 to 15    & 11.2 & 50.8 &  1.2 & 36.4 & 0.1 &     &      & 0.1 & 0.1 &     &     &      \\
Connective  & 15 to 129     & 10.0 & 16.3 &  4.3 & 68.4 & 0.4 &     &      & 0.4 & 0.3 &     &     &      \\
Bone 1      & 129 to 200    &  9.7 & 44.7 &  2.5 & 35.9 &     &     &  2.3 & 0.2 & 0.1 &     & 1.0 &  4.5 \\ 
Bone 2      & 200 to 300    &  9.1 & 41.4 &  2.7 & 36.8 &     & 0.1 &  3.2 & 0.2 & 0.1 &     & 1.0 &  6.3 \\ 
Bone 3      & 300 to 400    &  8.5 & 37.8 &  2.9 & 37.9 &     & 0.1 &  4.1 & 0.2 & 0.1 &     & 1.0 &  8.2 \\ 
Bone 4      & 400 to 500    &  8.0 & 34.5 &  3.1 & 38.8 &     & 0.1 &  5.0 & 0.2 & 0.1 &     & 1.0 & 10.0 \\ 
Bone 5      & 500 to 600    &  7.5 & 31.6 &  3.2 & 39.7 &     & 0.1 &  5.8 & 0.2 & 0.1 &     &     & 11.6 \\ 
Bone 6      & 600 to 700    &  7.1 & 28.7 &  3.4 & 40.4 &     & 0.1 &  6.6 & 0.2 & 0.1 &     &     & 13.1 \\ 
Bone 7      & 700 to 800    &  6.7 & 26.7 &  3.5 & 41.2 &     & 0.2 &  7.2 & 0.3 &     &     &     & 14.4 \\ 
Bone 8      & 800 to 900    &  6.3 & 24.7 &  3.7 & 41.8 &     & 0.2 &  7.8 & 0.3 &     &     &     & 15.7 \\ 
Bone 9      & 900 to 1000   &  6.0 & 22.7 &  3.8 & 42.4 &     & 0.2 &  8.4 & 0.3 &     &     &     & 16.8 \\ 
Bone 10     & 1000 to 1100  &  5.6 & 20.7 &  3.9 & 43.0 &     & 0.2 &  8.9 & 0.3 &     &     &     & 17.9 \\ 
Bone 11     & 1100 to 1200  &  5.3 & 18.7 &  4.0 & 43.5 &     & 0.2 &  9.4 & 0.3 &     &     &     & 18.9 \\ 
Bone 12     & 1200 to 1300  &  5.1 & 16.7 &  4.1 & 44.0 &     & 0.2 &  9.9 & 0.3 &     &     &     & 19.8 \\
Bone 13     & 1300 to 1400  &  4.8 & 15.7 &  4.2 & 44.4 &     & 0.2 & 10.3 & 0.3 &     &     &     & 20.7 \\
Bone 14     & 1400 to 1500  &  4.6 & 13.7 &  4.2 & 44.9 &     & 0.2 & 10.7 & 0.3 &     &     &     & 21.5 \\  
Bone 15     & > 1500        &  4.3 & 12.7 &  4.3 & 45.3 &     & 0.2 & 11.1 & 0.3 &     &     &     & 22.2 \\[1ex]
\hline
\end{tabular}
\label{table:ctmap}
\end{table}

@@

@@

@@

\section{GPU Acceleration}
GPUs are cool.

>>>>

Dose estimations have been made using many methodologies including

@@

\begin{sidewaystable}[ht]
\caption{Water Regions}
\centering 
\begin{tabular}{l c r r r r r r r r r r r r}
\hline \hline   
Media       & CT Range      & H    & C    & N    & O    & Na  & Mg  & P    & S   & Cl  & Ar  & K   & Ca \\ [0.5ex] 
\hline
Air         & -950 to -100  &      &      & 75.7 & 23.3 &     &     &      &     &     & 1.3 &     &      \\
Lung        & -1000 to -950 & 10.3 & 10.5 &  3.1 & 74.9 & 0.2 &     &  0.2 & 0.3 & 0.3 &     & 0.2 &      \\
Adipose     & -100 to 15    & 11.2 & 50.8 &  1.2 & 36.4 & 0.1 &     &      & 0.1 & 0.1 &     &     &      \\
Connective  & 15 to 129     & 10.0 & 16.3 &  4.3 & 68.4 & 0.4 &     &      & 0.4 & 0.3 &     &     &      \\
Bone 1      & 129 to 200    &  9.7 & 44.7 &  2.5 & 35.9 &     &     &  2.3 & 0.2 & 0.1 &     & 1.0 &  4.5 \\ 
Bone 2      & 200 to 300    &  9.1 & 41.4 &  2.7 & 36.8 &     & 0.1 &  3.2 & 0.2 & 0.1 &     & 1.0 &  6.3 \\ 
Bone 3      & 300 to 400    &  8.5 & 37.8 &  2.9 & 37.9 &     & 0.1 &  4.1 & 0.2 & 0.1 &     & 1.0 &  8.2 \\ 
Bone 4      & 400 to 500    &  8.0 & 34.5 &  3.1 & 38.8 &     & 0.1 &  5.0 & 0.2 & 0.1 &     & 1.0 & 10.0 \\ 
Bone 5      & 500 to 600    &  7.5 & 31.6 &  3.2 & 39.7 &     & 0.1 &  5.8 & 0.2 & 0.1 &     &     & 11.6 \\ 
Bone 6      & 600 to 700    &  7.1 & 28.7 &  3.4 & 40.4 &     & 0.1 &  6.6 & 0.2 & 0.1 &     &     & 13.1 \\ 
Bone 7      & 700 to 800    &  6.7 & 26.7 &  3.5 & 41.2 &     & 0.2 &  7.2 & 0.3 &     &     &     & 14.4 \\ 
Bone 8      & 800 to 900    &  6.3 & 24.7 &  3.7 & 41.8 &     & 0.2 &  7.8 & 0.3 &     &     &     & 15.7 \\ 
Bone 9      & 900 to 1000   &  6.0 & 22.7 &  3.8 & 42.4 &     & 0.2 &  8.4 & 0.3 &     &     &     & 16.8 \\ 
Bone 10     & 1000 to 1100  &  5.6 & 20.7 &  3.9 & 43.0 &     & 0.2 &  8.9 & 0.3 &     &     &     & 17.9 \\ 
Bone 11     & 1100 to 1200  &  5.3 & 18.7 &  4.0 & 43.5 &     & 0.2 &  9.4 & 0.3 &     &     &     & 18.9 \\ 
Bone 12     & 1200 to 1300  &  5.1 & 16.7 &  4.1 & 44.0 &     & 0.2 &  9.9 & 0.3 &     &     &     & 19.8 \\
Bone 13     & 1300 to 1400  &  4.8 & 15.7 &  4.2 & 44.4 &     & 0.2 & 10.3 & 0.3 &     &     &     & 20.7 \\
Bone 14     & 1400 to 1500  &  4.6 & 13.7 &  4.2 & 44.9 &     & 0.2 & 10.7 & 0.3 &     &     &     & 21.5 \\  
Bone 15     & > 1500        &  4.3 & 12.7 &  4.3 & 45.3 &     & 0.2 & 11.1 & 0.3 &     &     &     & 22.2 \\[1ex]
\hline
\end{tabular}
\label{table:ctmap}
\end{sidewaystable}

@@

Monte Carlo codes such as TOPAS and Geant4 \citep{ref:agostinellis} are the gold standard \citep{ref:jiax}

Codes such as EGS4, its improved versions EGSnrc, and EGS5 \citep{ref:nelsonw}, and PENELOPE \citep{ref:salvatf} are all Monte Carlo and have shown very good results to experimental. But they are developed for high energy physics.

@@

There are many acceleration techniques available for discrete ordinates \citep{ref:efremenkod} that can increase speed by 15-30\%.

GPU methods exist for solar stuff at satellites.

The geometry has been extended to Non-Uniform Rational B-Splins (NURBS) for reactor eigenvalue problems.

@@

\section{GPU Acceleration}

Monte Carlo dose computation for protons has been accelerated by GPU technology \citep{ref:jiax} and

Monte Carlo in voxelized geometries has been done by \citep{ref:hissoinys} for monoenergetic beams.
GPUs are cool.
